---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

 
## Loading and preprocessing the data
Extract the activity.cvs file from activity.zip,  
created data.frame from the csv file and wrap the data frame into a data table
```{r loaddata,  message=FALSE}
library(data.table)
library(dplyr)
activity <- data.table(read.csv(unz("activity.zip","activity.csv"))) %>%
            mutate(fulldate = strptime(date, format="%Y-%m-%d") + (interval %/% 100) * 60 + interval %% 100)  
``` 

## What is mean total number of steps taken per day?
Group the data by day, and summerize the steps by date. 
For dates that do not have steps, the number of steps is set to zero
```{r results="asis"}  
library(xtable)
number.of.steps.by.day <- activity %>% 
                          group_by(date) %>% 
                          summarise_each(funs(sum(., na.rm = TRUE)), steps)
```                          

In the historgram the number of steps per day are show  
```{r}
barplot( number.of.steps.by.day$steps, names.arg=number.of.steps.by.day$date, 
         ylab="Number of steps per day")
```

```{r}
mean.steps <- mean(number.of.steps.by.day$steps)
median.steps <- median(number.of.steps.by.day$steps)
```
The mean number of step per day is `r mean.steps` steps per day.  
The median is `r median.steps` steps per day.


## What is the average daily activity pattern?
```{r}
library(ggplot2)
library(scales)
mean.steps <- mean(activity$steps, na.rm = TRUE)
p <- qplot(activity$fulldate, activity$steps, geom="line") +scale_x_datetime(breaks = date_breaks("10 days"))
p <- p + geom_abline(intercept = mean.steps, slope = 0, colour ="red")
print(p)
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?









To create a histogram on a day basis, the precentage steps per day relative to the total number of steps has to be calculated, 
```{r}
# total.number.of.steps <-sum(activity$steps, na.rm = TRUE)
# number.of.steps.by.day <- mutate(number.of.steps.by.day, percentage = steps / total.number.of.steps * 100)
```



